Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2017-10-27 paper/main.tex
Small change to conclusion

\section{Conclusion}
Parallel linear recurrence can accelerate existing RNNs and be used in the design
of new architectures such as the GILR-LSTM. Parallel linear recurrence enables
rapid training with small minibatches, which further enables training models on
extremely long sequence lengths.
Our CUDA kernel is up to 40 times faster than a serial kernel on
sequence lengths of 65,536, and this benefit transfers to implemented models,
speeding up the SRU \cite{lei2017} by a factor of 9. The impressive results in
\cite{lei2017} and other recent work comprehensively show that
linear RNNs are, in many respects, equally as powerful as nonlinear
LSTMs. Our results on the synthetic example continue this trend, showing that
the GILR-LSTM is able to handle sequence length regimes that are longer than any
we have seen seriously suggested in the literature. We feel that the framework
of describing linear RNNs as linear surrogates for nonlinear RNNs is a fruitful
approach, and that this, paired with the PLR algorithm, will substantially
advance the ability to train RNNs, and to understand timeseries data.

>>>>

\section{Conclusion}
Parallel linear recurrence can accelerate existing RNNs and be used in the design
of new architectures such as the GILR-LSTM. Parallel linear recurrence enables
rapid training with small minibatches, which further enables training models on
extremely long sequence lengths.
The impressive results in
\cite{lei2017} and other recent work comprehensively show that
linear RNNs can often be used in place of traditional non-linear RNNs.
Our results on the synthetic example continue this trend, showing that
the GILR-LSTM is able to handle sequence length regimes that are longer than any
we have seen seriously suggested in the literature. We feel that the framework
of describing linear RNNs as linear surrogates for nonlinear RNNs is a fruitful
approach, and that this, paired with the PLR algorithm, will substantially
advance the ability to train RNNs, and to understand timeseries data.
